A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-29 rr-flow.Rmd
revised examples

We provide a reproducible analysis as working example via github as a testbed for users. The example shows a minimalistic analysis of the 'Considerations of Future Consequences (CFC) Scale'. The analysis demonstrates a succesful implementation of our workflow including downloading external data, comparing their state using a checksum, and running a confirmatory factor analysis on the first few items using lavaan [@lavaan2012]. Once all mentioned tools are installed on a computer, the following few steps are necessary to reproduce our analysis:

```{bash}

TODO: Aaron

```

@@

The overarching goal of this paper was to provide an easy to use workflow, that allows confidence in reproducibility. This workflow can be almost unfailingly trusted to be replicable with the following commands:

>>>>

The overarching goal of this paper was to provide an easy to use workflow, that allows confidence in reproducibility. T
We provide a reproducible analysis as working example via github as a testbed for users. The example shows a minimalistic analysis of the 'Considerations of Future Consequences (CFC) Scale'. The analysis demonstrates a succesful implementation of our workflow including downloading external data, comparing their state using a checksum, and running a confirmatory factor analysis on the first few items using lavaan [@lavaan2012]. Once all mentioned tools are installed on a computer, the following few steps are necessary to reproduce our analysis:

```{bash, eval=FALSE}

TODO: Aaron
git clone https://github.com/aaronpeikert/reproducible-research-example.git
cd reproducible-research-example
make build
make all DOCKER=TRUE
```

Similarly, this manuscript and the differing results across R versions were created using the proposed workflow and can be reproduced directly from out github repository:

@@
